Tree size, exposure, and hydraulic traits interactively shape drought response in a temperate broadleaf forest

### 2019-06-30 manuscript/04-results.Rmd
Update 04-results.Rmd
Updated to show r2 values in table with coefficients

## [1- tree size and exposure]
We evaluated the predictions outlined in the introduction
P1.0. Drought resistance decreased with DBH at time of drought.
P1.1. Drought resistance decreased with height at time of drought.
P1.2. Trees currently in a dominant crown position suffered more during drought. Intermediate and suppressed trees also suffered more (in model with height)
P1.3. Resistance was independent of elevation and distance from stream.

``` {r, biophysical-model, eval=TRUE, echo=FALSE, message=FALSE, cache=TRUE}
library(lme4)
library(AICcmodavg) #aictab function
library(car)
library(data.table)
library(knitr)
library(kableExtra)

trees_all_bio <- read.csv("tables_figures/trees_all_bio.csv", stringsAsFactors = FALSE)

@@

best <- lmm_all[[8]]
cof_bio <- data.frame("value" = coef(summary(best))[ , "Estimate"])
cof_bio <- setDT(cof_bio, keep.rownames = TRUE)[]
setnames(cof_bio, old="rn", new="coefficients")

```
``` {r, full-model, eval=TRUE, echo=FALSE, message=FALSE, cache=TRUE}
trees_all_full <- read.csv("tables_figures/trees_all_full.csv", stringsAsFactors = FALSE)

@@

best <- lmm_all[[121]]
cof_full <- data.frame("value" = coef(summary(best))[ , "Estimate"])
cof_full <- setDT(cof_full, keep.rownames = TRUE)[]
setnames(cof_full, old="rn", new="coefficients")
```
```{r, make-tables, eval=TRUE, echo=FALSE, message=FALSE, results = 'asis'}
library(knitr)
library(kableExtra)

>>>>

## 1- tree size and exposure
We evaluated the predictions outlined in the introduction
P1.0. Drought resistance decreased with DBH at time of drought.
P1.1. Drought resistance decreased with height at time of drought.
P1.2. Trees currently in a dominant crown position suffered more during drought. Intermediate and suppressed trees also suffered more (in model with height)
P1.3. Resistance was independent of elevation and distance from stream.

[**HYPOTHESIS TESTING TABLE**]

## 2- traits

``` {r, biophysical-model, eval=TRUE, echo=FALSE, message=FALSE, cache=TRUE}
library(lme4)
library(AICcmodavg) #aictab function
library(car)
library(piecewiseSEM)
library(data.table)
library(knitr)
library(kableExtra)

trees_all_bio <- read.csv("tables_figures/trees_all_bio.csv", stringsAsFactors = FALSE)
trees_all_bio$year <- as.character(trees_all_bio$year)

@@

best <- lmm_all[[8]]
cof_bio <- data.frame("value" = coef(summary(best))[ , "Estimate"])
cof_bio <- setDT(cof_bio, keep.rownames = TRUE)[]
setnames(cof_bio, old="rn", new="coefficients")
r <- rsquared(best)
r <- r[, c(1,6)]
r$Response <- as.character(r$Response)
r[1,1] <- "r^2"
setnames(r, old=c("Response", "Conditional"), new=c("coefficients", "value"))
cof_bio <- rbind(cof_bio, r)
```
``` {r, full-model, eval=TRUE, echo=FALSE, message=FALSE, cache=TRUE}
trees_all_full <- read.csv("tables_figures/trees_all_full.csv", stringsAsFactors = FALSE)
trees_all_full$year <- as.character(trees_all_full$year)

@@

best <- lmm_all[[100]]
cof_full <- data.frame("value" = coef(summary(best))[ , "Estimate"])
cof_full <- setDT(cof_full, keep.rownames = TRUE)[]
setnames(cof_full, old="rn", new="coefficients")
r <- rsquared(best)
r <- r[, c(1,6)]
r$Response <- as.character(r$Response)
r[1,1] <- "r^2"
setnames(r, old=c("Response", "Conditional"), new=c("coefficients", "value"))
cof_full <- rbind(cof_full, r)
```
```{r, make-tables, eval=TRUE, echo=FALSE, message=FALSE, results = 'asis'}
library(knitr)
library(kableExtra)
